### 2018-07-20 chapters/02-background/math-background.tex
Update introduction with more important information

\section{Mathematical Background}\label{sec:math-background}
To understand the following chapters in the thesis, we need a brief introduction in complex analysis and multivalued functions. The following mathematical introduction is based on the book \textit{Introduction to Complex Analysis} by H.~A.~Priestley~\cite{ComplexAna:Intro}.

A complex number $z \in \Complex$ is specified by a two real numbers $x$ and $y$ as $z = x+y\iunit$, with $\iunit$ as the imaginary unit, which is defined as a solution of $\iunit^2 = -1$. The two real numbers are called the real part $x = \Re(z)$ and the imaginary part $y = \Im(z)$ of $z$. It is convenient to represent complex numbers as points in a $\Real^2$ plane, which is called \textbf{complex plane}. We identify $z = x+y\iunit$ as $(x,y) \in \Real^2$ in the complex plane. It is sometimes useful to represent complex numbers by polar coordinates and write $x = r\cos@@{\phi}$ and $y = r\sin@@{\phi}$, with $r \geq 0$ and $\phi \in \Real$. Since $\cos@@{\phi}+\sin@@{\phi}\iunit$ can be written as $\expe^{\iunit\phi}$, we write $z = x+y\iunit$ in polar coordinates as $z = r\expe^{\iunit\phi}$. The angle $\phi$ is often called the \textbf{phase} (or argument) of $z$ and $r$ is the absolute value of $z$. Similar to $\Re(z)$ for the real part and $\Im(z)$ for the imaginary part of $z$, we can access $r = |z|$ and $\phi = \ph@{z}$.\footnote{Note that the phase of $z$ is often called the \textbf{argument} of $z$. Therefore, in CAS the phase function is often the \texttt{argument} function.}

\begin{figure}[ht]
    \centering
    \subfloat[Four color phase mapping.]{%
        \includegraphics[width=0.28\textwidth]{dlmfColorMap.png}
        \label{fig:four-color}%
    }
    \hspace{0.4cm}
    \subfloat[Continues phase mapping in \DLMF.]{%
        \includegraphics[width=0.28\textwidth]{dlmfColorMapCont.png}
        \label{fig:cont-color}%
    }
    \hspace{0.4cm}
    \subfloat[Continues phase mapping in \Maple.]{%
        \includegraphics[width=0.28\textwidth]{mapleColorMap.png}
        \label{fig:maple-color}%
    }
    \caption{Three different domain coloring methods. Mappings~\protect\subref{fig:four-color} and \protect\subref{fig:cont-color} used in the \DLMF{} (Source: \DLMF{~}\cite{NIST:DLMF} in help page, \textit{About Color Map}). Mapping~\protect\subref{fig:maple-color} is the default coloring map in \Maple.}
    \label{fig:domain-coloring}
\end{figure}

Since the same basic arithmetical rules apply in $\Complex$ as in $\Real$, we will not introduce all arithmetical rules for complex numbers here. However, another interesting part are plots of complex functions. Consider a function $f: \Complex \mapsto \Complex$. This can be considered as $f: \Real^2 \mapsto \Real^2$, which shows us four real dimensions that need to be displayed in a three-dimensional space. The most common solution to plot those four dimensions is called domain coloring. With this technique, each value in the complex plane is represented by a color. There is no standard method to map complex values to colors. A simple method is to map a unique color for each of the quadrants in the complex plane (used in the DLMF). Another variation are continues phase mappings, which use color wheels. In those cases, $\phi$ represents the hue and optionally $r$ defines the intensity of the hue. The second variation is mostly used in \gls{cas}, but there is no standard for the orientation of the color wheel. Figure~\ref{fig:domain-coloring} draws three different examples.

This thesis mostly focus on the \gls{cas} \Maple, therefore all of the following complex plots use the default color map in \Maple{~}\ref{fig:maple-color}.

A three-dimensional plot of a complex function, such as $f$ from above, usually maps the real and imaginary part of the variable to the $x$ and $y$ axes, while the height is defined by the absolute value of the complex variable $|z|$. Figure~\ref{fig:cylinderU} demonstrates a complex plot of the parabolic cylinder function $U(a,z)$~\cite[(12.2i)]{NIST:DLMF} in \Maple.

\begin{figure}[ht]
	\centering
	\includegraphics[width=0.8\textwidth]{cylinderUPlot.png}
	\caption{A 3-dimensional complex plot of the parabolic cylinder function $U(a,z)$ at $a=0$ plotted by \Maple.~\cite[(12.2i)]{NIST:DLMF}}
	\label{fig:cylinderU}
\end{figure}

Another way to plot such complex functions is to plot the real and imaginary parts of the solution separately. Figure~\ref{fig:cylinderUSplit} illustrates this plotting method for the parabolic cylinder function again.

Note that for real function plots, such separate plots for the imaginary and real values of a complex function, will use a color map as well. In that case, the color map is just an adornment and has nothing to do with complex color maps. Figure~\ref{fig:cylinderUSplit} illustrates the separate plots for real and imaginary values for the parabolic cylinder function again.

\begin{figure}[!htp]
    \centering
    \subfloat[Plot of the real value of $\ParabolicU@{0}{z}$.]{%
        \includegraphics[width=0.8\textwidth]{cylinderURe.png}
        \label{fig:cylinderURe}%
    }
    \vspace{-0.1cm}
    \subfloat[Plot of the imaginary value of $\ParabolicU@{0}{z}$.]{%
        \includegraphics[width=0.8\textwidth]{cylinderUIm.png}
        \label{fig:cylinderUIm}%
    }
    \caption{Separately plot of the real~\protect\subref{fig:cylinderURe} and imaginary~\protect\subref{fig:cylinderUIm} part of the parabolic cylinder function $U(a,z)$ at $a=0$.}
    \label{fig:cylinderUSplit}
\end{figure}

\subsection{Multivalued Functions}
The following definitions for multivalued functions are based on \textit{Complex Variables}~\cite{ComplexVariables} by M.~J.~Ablowitz and A.~S.~Fokas.

Unlike a typical\footnote{In lack of a better word to distinguish single-valued and multivalued functions, we call single-valued functions here typical functions, because these functions are best known.} function, multivalued functions associate not only one output to any particular input, but a whole set of output values. A real-valued example is the square root function, which associates for each positive real number two real square roots. For example\footnote{Note that the radical sign $\sqrt{}$\ is defined for the principal square roots, which are the unique non-negative square roots. Therefore, $\sqrt{4}$ is always $2$, and not $-2$. However, the solutions of the square root of a positive number $a$ are $\left\{+\sqrt{a},-\sqrt{a}\right\}$.}, the solution of $4^{\frac{1}{2}}$ is $\{+2,-2\}$.

Consider now the natural logarithm with complex arguments and $z = r\expe^{\iunit\phi}$ in polar coordinates. Since it is the natural logarithm, $\ln@{z} = \ln@{r} + \iunit\phi$ and the imaginary part is just $\phi$. Let $r = 1$, so that $z$ is on the unit circle for all $\phi$. Let be $z_1$ the complex number for $\phi = 0$ and $z_2$ the complex number for $\phi = 2\cpi$. Obviously $z_1 = z_2$ but $\ln@{z_1} \neq \ln@{z_2}$. Therefore, the natural logarithm is also multivalued and has an infinite number of solutions for $\ln@{z}$.

@@

Defining branch cuts to allow analytic computations on the principal branches is a common task for \gls{cas}~\cite{Maple:Cuts}. Unfortunately, the position of the branch cuts is not well-defined. Indeed, consider $\phi \in [-\cpi,\cpi)$ instead of $\phi \in [0,2\cpi)$ and define the branch cut at $(-\infty, 0)$; than the branch is also continues and single-valued.

In general a branch cut is a curve which ends can be possibly open, half-open or closed. A branch cut can be also defined in a more complicated shape (e.g. spirals). Most of the multivalued functions have standard, convenient positions for the branch cuts, which are commonly accepted. The branch cut at $(-\infty, 0]$ for the complex square root function is one of those standard positions. However, the positions can vary from system to system~\cite{Branches:acot}.

@@

\subsection{Elementary \& Special Functions}\label{subsec:special-functions}
A function is called \textbf{elementary} if it can be constructed using only a finite combination of constant functions, field operations, and algebraic, trigonometric, exponential, and logarithmic functions together with their inverses~\cites{Elementary:1}[145]{Elementary:2}.

@@

For example, in 1964 Milton Abramowitz and Irene A. Stegun published the \textit{Handbook of Mathematical Functions with Formulas, Graphs, and Mathematical Tables}~\cite{AbramowitzStegun} at \gls{nist}\footnote{In 1988 the \textit{National Bureau of Standards} (NBS) was renamed to the \textit{National Instutute of Standards and Technology} (NIST).}. The handbook became the most comprehensive source of information on special functions. Therefore, the \gls{nist} has published a new version called \textit{NIST Handbook of Mathematical Function}~\cite{NIST:Handbook} in 2010 to replace the predecessor.

Because there is no formal definition for special functions, some problems appear for our translator project. For example the \textit{Encyclop\ae{dia} Britannica} wrote:
\begin{myQuote}{Encyclop\ae{dia} Britannica - Special function~\cite{SpecialFunctions:britannica}}
	Special function, any of a class of mathematical functions that arise in the solution of various classical problems of physics. [...] Different scientists might not completely agree on which functions are to be included among the special functions, although there would certainly be very substantial overlap.
\end{myQuote}

In \textit{Special Functions}~\cite{SF:Book}, G.~E.~Andrews~et~al. wrote in the preface:
\begin{myQuote}{Special Functions - Preface~\cite{SF:Book}}
Paul Tur\'an once remarked that special functions would be more appropriately labeled "useful functions".
\end{myQuote}

Our reference for special functions in this thesis will be the \textit{NIST Handbook of Mathematical Function} and its digital counterpart the \gls{dlmf}~\cite{NIST:DLMF}. See the later section~\ref{sec:dlmf} for a more detailed explanation.

Since most of the special functions represent solutions for other mathematical expressions, they were intensively studied - mostly in applied mathematics. In the past, huge tables of values were used for calculations~\cite{Tables}. Therefore, the book by Abramowitz and Stegun also contains tables with values for several special functions~\cite{AbramowitzStegun}. Obviously, computations of special functions with \gls{cas} were desired. Therefore, \gls{cas} support numerous of special functions. However, all \gls{cas} contain its own ever growing lists of them. Sometimes they use the same definitions, domains and position of branch cuts as defined the handbooks, sometimes not. A translator needs to pay attention to those differences as well. Otherwise the translation process could produce unexpected effects. One of these effects can be produced by different positions of branch cuts in the systems. The next section will give some examples and explanations of these problems.

\subsection{Problems of Branch Cuts}\label{subsec:branch-cut-issues}
Obviously, different positions of branch cuts can cause problems, if we transfer a function from one system to the other. Those differences can even appear in well-known elementary functions. For example, the \gls{dlmf} defines the branch cut for the inverse cotangent function~\cite[(4.23.9)]{NIST:DLMF} at $[-\iunit, \iunit]$, while \Maple{} reasonably~\cite{Branches:acot} defines the branch cut at $(-\infty\iunit, -\iunit]$ and $[\iunit, \infty\iunit)$. Figure~\ref{fig:acot} illustrates the problem. A scientist, who is familiar with the definition for the branch cut by the \gls{dlmf} would assume an output such as in figure~\ref{fig:acotCont}, but get an output such as in figure~\ref{fig:acotJump} in \Maple.

@@

We provide the following solution for such problems. Instead of translating the function itself, the translator uses other equivalent representations for the function. In case of the arccotangent function, we can use the following alternative representations, based on the suggestions in~\cite{Branches:acot}.

@@

A more complicated example might be the equation of the already introduced parabolic cylinder function $U(a,z)$ and the modified Bessel function of the second kind $\BesselK{\nu}@{z}$. The parabolic cylinder function is a solution of a second order differential equation~\cite[(12.2i)]{NIST:DLMF} and can be represented by $\BesselK{\nu}@@{z}$ for $a=0$. The relation is defined in~(\ref{eq:branch-cut-issue}).

@@

Since \gls{cas} do not provide Riemann surfaces, we use another approach to solve this problem, called \textbf{analytic continuation}. Analytic continuation is the process of extending the range of validity of a representation or more generally extending the region of definition of an analytic function~\cite[152]{ComplexVariables}. For the modified Bessel function of the second kind the analytic continuation is defined in the \gls{dlmf}~\cite[(10.34.4)]{NIST:DLMF}. With analytic continuation, the right hand side of equation~(\ref{eq:branch-cut-issue}) is illustrated in figure~\ref{fig:analytic-cont}.

@@

Mathematical expressions can be represented by ordered trees consisting of terminal symbols, such as identifiers or numbers (leaf nodes), and functions or operators (non-leaf nodes)~\cite{VMEXT}. Consider the mathematical expression
\begin{equation}\label{eq:simple-expr}
\expe^{x} + \frac{x^2}{\cpi}.
\end{equation}

The tool \gls{vmext}~\cite{VMEXT} visualizes expression trees. Figure~\ref{fig:simple-expr-tree} draws the expression tree for (\ref{eq:simple-expr}).

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{expressionTreeSimple.png}
    \caption{The expression tree of (\ref{eq:simple-expr}) visualized with VMEXT~\cite{VMEXT}.}
    \label{fig:simple-expr-tree}
\end{figure}

>>>>

%\section{Mathematical Background}\label{sec:math-background}
%To understand the following chapters in the thesis, we need a brief introduction in complex analysis and multivalued functions. The following mathematical introduction is based on the book \textit{Introduction to Complex Analysis} by H.~A.~Priestley~\parencite{ComplexAna:Intro}.

%A complex number $z \in \Complex$ is specified by a two real numbers $x$ and $y$ as $z = x+y\iunit$, with $\iunit$ as the imaginary unit, which is defined as a solution of $\iunit^2 = -1$. The two real numbers are called the real part $x = \Re(z)$ and the imaginary part $y = \Im(z)$ of $z$. It is convenient to represent complex numbers as points in a $\Real^2$ plane, which is called \textbf{complex plane}. We identify $z = x+y\iunit$ as $(x,y) \in \Real^2$ in the complex plane. It is sometimes useful to represent complex numbers by polar coordinates and write $x = r\cos@@{\phi}$ and $y = r\sin@@{\phi}$, with $r \geq 0$ and $\phi \in \Real$. Since $\cos@@{\phi}+\sin@@{\phi}\iunit$ can be written as $\expe^{\iunit\phi}$, we write $z = x+y\iunit$ in polar coordinates as $z = r\expe^{\iunit\phi}$. The angle $\phi$ is often called the \textbf{phase} (or argument) of $z$ and $r$ is the absolute value of $z$. Similar to $\Re(z)$ for the real part and $\Im(z)$ for the imaginary part of $z$, we can access $r = |z|$ and $\phi = \ph@{z}$.\footnote{Note that the phase of $z$ is often called the \textbf{argument} of $z$. Therefore, in CAS the phase function is often the \texttt{argument} function.}

%\begin{figure}[ht]
%    \centering
%    \subfloat[Four color phase mapping.]{%
%        \includegraphics[width=0.28\textwidth]{dlmfColorMap.png}
%        \label{fig:four-color}%
%    }
%    \hspace{0.4cm}
%    \subfloat[Continues phase mapping in \DLMF.]{%
%        \includegraphics[width=0.28\textwidth]{dlmfColorMapCont.png}
%        \label{fig:cont-color}%
%    }
%    \hspace{0.4cm}
%    \subfloat[Continues phase mapping in \Maple.]{%
%        \includegraphics[width=0.28\textwidth]{mapleColorMap.png}
%        \label{fig:maple-color}%
%    }
%    \caption{Three different domain coloring methods. Mappings~\protect\subref{fig:four-color} and \protect\subref{fig:cont-color} used in the \DLMF{} (Source: \DLMF{~}\parencite{NIST:DLMF} in help page, \textit{About Color Map}). Mapping~\protect\subref{fig:maple-color} is the default coloring map in \Maple.}
%    \label{fig:domain-coloring}
%\end{figure}

%Since the same basic arithmetical rules apply in $\Complex$ as in $\Real$, we will not introduce all arithmetical rules for complex numbers here. However, another interesting part are plots of complex functions. Consider a function $f: \Complex \mapsto \Complex$. This can be considered as $f: \Real^2 \mapsto \Real^2$, which shows us four real dimensions that need to be displayed in a three-dimensional space. The most common solution to plot those four dimensions is called domain coloring. With this technique, each value in the complex plane is represented by a color. There is no standard method to map complex values to colors. A simple method is to map a unique color for each of the quadrants in the complex plane (used in the DLMF). Another variation are continues phase mappings, which use color wheels. In those cases, $\phi$ represents the hue and optionally $r$ defines the intensity of the hue. The second variation is mostly used in \gls{cas}, but there is no standard for the orientation of the color wheel. Figure~\ref{fig:domain-coloring} draws three different examples.

%This thesis mostly focus on the \gls{cas} \Maple, therefore all of the following complex plots use the default color map in \Maple{~}\ref{fig:maple-color}.

%A three-dimensional plot of a complex function, such as $f$ from above, usually maps the real and imaginary part of the variable to the $x$ and $y$ axes, while the height is defined by the absolute value of the complex variable $|z|$. Figure~\ref{fig:cylinderU} demonstrates a complex plot of the parabolic cylinder function $U(a,z)$~\parencite[(12.2i)]{NIST:DLMF} in \Maple.

%\begin{figure}[ht]
%	\centering
%	\includegraphics[width=0.8\textwidth]{cylinderUPlot.png}
%	\caption{A 3-dimensional complex plot of the parabolic cylinder function $U(a,z)$ at $a=0$ plotted by \Maple.~\parencite[(12.2i)]{NIST:DLMF}}
%	\label{fig:cylinderU}
%\end{figure}

%Another way to plot such complex functions is to plot the real and imaginary parts of the solution separately. Figure~\ref{fig:cylinderUSplit} illustrates this plotting method for the parabolic cylinder function again.

%Note that for real function plots, such separate plots for the imaginary and real values of a complex function, will use a color map as well. In that case, the color map is just an adornment and has nothing to do with complex color maps. Figure~\ref{fig:cylinderUSplit} illustrates the separate plots for real and imaginary values for the parabolic cylinder function again.

%\begin{figure}[!htp]
%    \centering
%    \subfloat[Plot of the real value of $\ParabolicU@{0}{z}$.]{%
%        \includegraphics[width=0.8\textwidth]{cylinderURe.png}
%        \label{fig:cylinderURe}%
%    }
%    \vspace{-0.1cm}
%    \subfloat[Plot of the imaginary value of $\ParabolicU@{0}{z}$.]{%
%        \includegraphics[width=0.8\textwidth]{cylinderUIm.png}
%        \label{fig:cylinderUIm}%
%    }
%    \caption{Separately plot of the real~\protect\subref{fig:cylinderURe} and imaginary~\protect\subref{fig:cylinderUIm} part of the parabolic cylinder function $U(a,z)$ at $a=0$.}
%    \label{fig:cylinderUSplit}
%\end{figure}

%\subsection{Multivalued Functions}
%The following definitions for multivalued functions are based on \textit{Complex Variables}~\parencite{ComplexVariables} by M.~J.~Ablowitz and A.~S.~Fokas.

%Unlike a typical\footnote{In lack of a better word to distinguish single-valued and multivalued functions, we call single-valued functions here typical functions, because these functions are best known.} function, multivalued functions associate not only one output to any particular input, but a whole set of output values. A real-valued example is the square root function, which associates for each positive real number two real square roots. For example\footnote{Note that the radical sign $\sqrt{}$\ is defined for the principal square roots, which are the unique non-negative square roots. Therefore, $\sqrt{4}$ is always $2$, and not $-2$. However, the solutions of the square root of a positive number $a$ are $\left\{+\sqrt{a},-\sqrt{a}\right\}$.}, the solution of $4^{\frac{1}{2}}$ is $\{+2,-2\}$.

%Consider now the natural logarithm with complex arguments and $z = r\expe^{\iunit\phi}$ in polar coordinates. Since it is the natural logarithm, $\ln@{z} = \ln@{r} + \iunit\phi$ and the imaginary part is just $\phi$. Let $r = 1$, so that $z$ is on the unit circle for all $\phi$. Let be $z_1$ the complex number for $\phi = 0$ and $z_2$ the complex number for $\phi = 2\cpi$. Obviously $z_1 = z_2$ but $\ln@{z_1} \neq \ln@{z_2}$. Therefore, the natural logarithm is also multivalued and has an infinite number of solutions for $\ln@{z}$.

@@

Defining branch cuts to allow analytic computations on the principal branches is a common task for \gls{cas}~\parencite{Maple:Cuts}. Unfortunately, the position of the branch cuts is not well-defined. Indeed, consider $\phi \in [-\cpi,\cpi)$ instead of $\phi \in [0,2\cpi)$ and define the branch cut at $(-\infty, 0)$; than the branch is also continues and single-valued.

In general a branch cut is a curve which ends can be possibly open, half-open or closed. A branch cut can be also defined in a more complicated shape (e.g. spirals). Most of the multivalued functions have standard, convenient positions for the branch cuts, which are commonly accepted. The branch cut at $(-\infty, 0]$ for the complex square root function is one of those standard positions. However, the positions can vary from system to system~\parencite{Branches:acot}.

@@

\subsection{Elementary \& Special Functions}\label{subsec:special-functions}
A function is called \textbf{elementary} if it can be constructed using only a finite combination of constant functions, field operations, and algebraic, trigonometric, exponential, and logarithmic functions together with their inverses~\parencites{Elementary:1}[145]{Elementary:2}.

@@

For example, in 1964 Milton Abramowitz and Irene A. Stegun published the \textit{Handbook of Mathematical Functions with Formulas, Graphs, and Mathematical Tables}~\parencite{AbramowitzStegun} at \gls{nist}\footnote{In 1988 the \textit{National Bureau of Standards} (NBS) was renamed to the \textit{National Instutute of Standards and Technology} (NIST).}. The handbook became the most comprehensive source of information on special functions. Therefore, the \gls{nist} has published a new version called \textit{NIST Handbook of Mathematical Function}~\parencite{NIST:Handbook} in 2010 to replace the predecessor.

Because there is no formal definition for special functions, some problems appear for our translator project. For example the \textit{Encyclop\ae{dia} Britannica} wrote:
\begin{myQuote}{Encyclop\ae{dia} Britannica - Special function~\parencite{SpecialFunctions:britannica}}
	Special function, any of a class of mathematical functions that arise in the solution of various classical problems of physics. [...] Different scientists might not completely agree on which functions are to be included among the special functions, although there would certainly be very substantial overlap.
\end{myQuote}

In \textit{Special Functions}~\parencite{SF:Book}, G.~E.~Andrews~et~al. wrote in the preface:
\begin{myQuote}{Special Functions - Preface~\parencite{SF:Book}}
Paul Tur\'an once remarked that special functions would be more appropriately labeled "useful functions".
\end{myQuote}

Our reference for special functions in this thesis will be the \textit{NIST Handbook of Mathematical Function} and its digital counterpart the \gls{dlmf}~\parencite{NIST:DLMF}. See the later section~\ref{sec:dlmf} for a more detailed explanation.

Since most of the special functions represent solutions for other mathematical expressions, they were intensively studied - mostly in applied mathematics. In the past, huge tables of values were used for calculations~\parencite{Tables}. Therefore, the book by Abramowitz and Stegun also contains tables with values for several special functions~\parencite{AbramowitzStegun}. Obviously, computations of special functions with \gls{cas} were desired. Therefore, \gls{cas} support numerous of special functions. However, all \gls{cas} contain its own ever growing lists of them. Sometimes they use the same definitions, domains and position of branch cuts as defined the handbooks, sometimes not. A translator needs to pay attention to those differences as well. Otherwise the translation process could produce unexpected effects. One of these effects can be produced by different positions of branch cuts in the systems. The next section will give some examples and explanations of these problems.

\subsection{Problems of Branch Cuts}\label{subsec:branch-cut-issues}
Obviously, different positions of branch cuts can cause problems, if we transfer a function from one system to the other. Those differences can even appear in well-known elementary functions. For example, the \gls{dlmf} defines the branch cut for the inverse cotangent function~\parencite[(4.23.9)]{NIST:DLMF} at $[-\iunit, \iunit]$, while \Maple{} reasonably~\parencite{Branches:acot} defines the branch cut at $(-\infty\iunit, -\iunit]$ and $[\iunit, \infty\iunit)$. Figure~\ref{fig:acot} illustrates the problem. A scientist, who is familiar with the definition for the branch cut by the \gls{dlmf} would assume an output such as in figure~\ref{fig:acotCont}, but get an output such as in figure~\ref{fig:acotJump} in \Maple.

@@

We provide the following solution for such problems. Instead of translating the function itself, the translator uses other equivalent representations for the function. In case of the arccotangent function, we can use the following alternative representations, based on the suggestions in~\parencite{Branches:acot}.

@@

A more complicated example might be the equation of the already introduced parabolic cylinder function $U(a,z)$ and the modified Bessel function of the second kind $\BesselK{\nu}@{z}$. The parabolic cylinder function is a solution of a second order differential equation~\parencite[(12.2i)]{NIST:DLMF} and can be represented by $\BesselK{\nu}@@{z}$ for $a=0$. The relation is defined in~(\ref{eq:branch-cut-issue}).

@@

Since \gls{cas} do not provide Riemann surfaces, we use another approach to solve this problem, called \textbf{analytic continuation}. Analytic continuation is the process of extending the range of validity of a representation or more generally extending the region of definition of an analytic function~\parencite[152]{ComplexVariables}. For the modified Bessel function of the second kind the analytic continuation is defined in the \gls{dlmf}~\parencite[(10.34.4)]{NIST:DLMF}. With analytic continuation, the right hand side of equation~(\ref{eq:branch-cut-issue}) is illustrated in figure~\ref{fig:analytic-cont}.

@@

Mathematical expressions can be represented by ordered trees consisting of terminal symbols, such as identifiers or numbers (leaf nodes), and functions or operators (non-leaf nodes)~\parencite{VMEXT}. Consider the mathematical expression
\begin{equation}\label{eq:simple-expr}
\expe^{x} + \frac{x^2}{\cpi}.
\end{equation}

The tool \gls{vmext}~\parencite{VMEXT} visualizes expression trees. Figure~\ref{fig:simple-expr-tree} draws the expression tree for (\ref{eq:simple-expr}).

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{expressionTreeSimple.png}
    \caption{The expression tree of (\ref{eq:simple-expr}) visualized with VMEXT~\parencite{VMEXT}.}
    \label{fig:simple-expr-tree}
\end{figure}

### 2018-07-20 chapters/02-background/related-work.tex
Update introduction with more important information

\section{Related Work}\label{sec:related-work}
Since \LaTeX{} became the de facto standard for writing papers in mathematics, most of the \gls{cas} nowadays are able to import and export mathematical \LaTeX{} expressions. Those tools have two essential problems. First of all, they cannot import mathematical expressions where the semantic information is absent, which is the usual case for generic \LaTeX{} expressions. Therefore, they are only able to import simple mathematical expressions, where the semantics are unique. For example, the internal \LaTeX{} macro \verb|\frac| always indicates a fraction. These import tools fail for more complex expressions, for example the Jacobi polynomial in \cref{tab:JacobiP-usecase}. The second problem appears in the export tools. Mathematical expressions in \gls{cas} are fully semantic, otherwise the \gls{cas} wouldn't be able to compute or evaluate the expressions. During the export process, the semantic information gets lost, because generic \LaTeX{} is not able to carry semantic information. In consequence of these two problems, an exported expression cannot be imported to the same system again in most cases (except those simple expressions described above). Our tool should solve these problems and provide round trip translations between \LaTeX{} and \gls{cas}.

>>>>

\section{Related Work}\label{sec:related-work}
Since \LaTeX{} became the de facto standard for writing papers in mathematics, most of the \gls{cas} provide simple functions to import and export mathematical \LaTeX{} expressions%
\footnote{The selected \gls{cas} Maple, Mathematica, Matlab, and SageMath provide import and/or export functions for \LaTeX:\\
Maple, \url{http://www.maplesoft.com/support/help/Maple/view.aspx?path=latex} seen 06/2017;\\
Mathematica, \url{https://reference.wolfram.com/language/tutorial/GeneratingAndImportingTeX.html} seen 06/2017;\\
Matlab, \url{https://www.mathworks.com/help/symbolic/latex.html} seen 06/2017;\\
SageMath, \url{http://doc.sagemath.org/html/en/tutorial/latex.html} seen 06/2017}. %
Those tools have two essential problems. First of all, they cannot import mathematical expressions where the semantic information is absent, which is the usual case for generic \LaTeX{} expressions. Therefore, they are only able to import simple mathematical expressions, where the semantics are unique. For example, the internal \LaTeX{} macro \verb|\frac| always indicates a fraction. These import tools fail for more complex expressions, for example the Jacobi polynomial in \cref{tab:JacobiP-usecase}. The second problem appears in the export tools. Mathematical expressions in \gls{cas} are fully semantic, otherwise the \gls{cas} wouldn't be able to compute or evaluate the expressions. During the export process, the semantic information gets lost, because generic \LaTeX{} is not able to carry semantic information. In consequence of these two problems, an exported expression cannot be imported to the same system again in most cases (except those simple expressions described above). Our tool should solve these problems and provide round trip translations between \LaTeX{} and \gls{cas}.

### 2018-07-20 chapters/03-translator/backward-trans.tex
Update introduction with more important information

The general walkthrough of our backward translation starts with a string of a \texttt{1D} \Maple{} input expression. As described above, this string is entered in \Maple{} to parse the expression and work on the nested list version of the \inertF{} afterwards. This causes some problems. Mostly because \Maple{} automatically evaluates input expressions immediately - even before we have a chance to take a look at the internal data structure of the input. For example, an input such as $\sin@{\frac{\cpi}{2}}$ is immediately evaluated to $1$ and the internal data structure just shows us the positive integer value $1$ instead of the trigonometric function.

>>>>

The general walkthrough of our backward translation starts with a string of a \texttt{1D} \Maple{} input expression. As described above, this string is entered in \Maple{} to parse the expression and work on the nested list version of the \inertF{} afterwards. This causes some problems. Mostly because \Maple{} automatically evaluates input expressions immediately - even before we have a chance to take a look at the internal data structure of the input. For example, an input such as $\sin\left(\frac{\cpi}{2}\right)$ is immediately evaluated to $1$ and the internal data structure just shows us the positive integer value $1$ instead of the trigonometric function.
